Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-07 main.tex
CP

\documentclass[conference]{IEEEtran}
\newif\ifdraft \drafttrue
\newif\iftext \draftfalse

@@

\section{Preliminaries}

\begin{itemize}
\item (A sketch of) the RISC-V machine model and operational semantics.
\item Reminder of the standard definition of NI.

@@

Designate sets of private and public addresses.

@@

\section{Tainting is (a bit less than) noninterference}

\begin{itemize}
\item First intuition: A program is taint-NI if every pair of runs that don’t
branch on high data are noninterfering in the standard sense.  (i.e., they
don't write secret data to public locations and vice versa)
\item Better alternative: … for every pair of runs that take the same control path (even if they branch on tainted data)...
\item \bcp{We could even go a step farther: {\em truncate} the runs at the
  first point where their PCs differ, then demand NI.}
\end{itemize}

\section{Stack protection is (a bit more than) noninterference}

@@

\section*{References}
\bibliographystyle{IEEEabrv}
\bibliography{bcp}
\bibliography{local}

>>>>

\documentclass[conference]{IEEEtran}
\newif\ifdraft \drafttrue
\newif\iftext \textfalse

@@

\section{Machine model}

(A sketch of) the RISC-V machine model and operational semantics.

Conventions:
%
\newcommand{\word}{W}
\newcommand{\addr}{A}
\newcommand{\WORDS}{{\mathcal W}}
\newcommand{\reg}{R}
\newcommand{\REGS}{{\mathcal R}}
\newcommand{\mach}{M}
\newcommand{\MACHS}{{\mathcal M}}
\newcommand{\PC}[1]{\mathit{PC}(#1)}
%
\begin{itemize}
\item Words / addresses: $\word,\addr \in \WORDS$
\item Registers: $\reg \in \REGS$
\item Machine states:
$\mach \in \MACHS = (\WORDS\rightarrow\WORDS,\, \REGS\rightarrow\WORDS,\,
\WORDS)$
\item Abbreviations: \\
$\mach(\addr) = \mach.1(\addr)$ \\
$\mach(\reg) = \mach.2(\reg)$ \\
$\mach(\textsc{pc}) = \mach.3$ \\
\end{itemize}

\section{Noninterference}

\begin{itemize}
\item We use the word {\em policy} for any kind of dynamic enforcement
mechanism (e.g., a runtime taint tracker, heap coloring rules, capability
hardware, etc.). We use {\em property} for a mathematical predicate on
programs (or machine states) capturing some useful security goal, e.g. noninterference.

\item Reminder of the standard definition of NI.

@@

Designate sets of private, internal, and public addresses.

@@

\section{Tainting is noninterference$-$}

\begin{itemize}
\item First intuition: A program is taint-NI if every pair of runs that don’t
branch on high data are noninterfering in the standard sense.  (i.e., they
don't write secret data to public locations and vice versa)
\item Better alternative: … for every pair of runs that take the same control path (even if they branch on tainted data)...
\item \bcp{We could even go a step farther: {\em truncate} the runs at the
  first point where their PCs differ, then demand NI.  This is a less
  demanding property and probably a less desirable one, as it doesn't
  predict the behavior of actual taint policies.  Discuss.}
\item (Are there any other variations of tainting that we could present in
this framework?)
\end{itemize}

\section{Separation is noninterference$+$}

\section{Stack protection is noninterference$++$}

@@

\section*{References}
\bibliographystyle{IEEEtran}
% \bibliography{bcp,local}
